---
title: 'Statistics are useless without suitable data: How to implement and assess for data quality'
author: "Erin M. Buchanan"
date: "7/9/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r import_data, include = F}
master <- read.csv("SIPS_DQ_data.csv", stringsAsFactors = F)

##reverse coded items
master[ , c("infrequent1", "infrequent4", "infrequent5")] <- 6 - master[ , c("infrequent1", "infrequent4", "infrequent5")]
master$mlq9 <- 8 - master$mlq9

##scoring
master$flexibility <- apply(master[ , 28:39], 1, sum)
master$inflexibility <- apply(master[, 45:56], 1, sum)
master$resiliency <- apply(master[ , 62:75], 1, sum)
master$purpose <- apply(master[ , c(81, 84, 85, 86, 89)], 1, sum)
master$search <- apply(master[ , c(82, 83, 87, 88, 90)], 1, sum)

##clear out unfinished
master <- subset(master, Finished == 1)
```

## DQ STUFF

## Where to put DQ checks? 

## Real Example!

- Question: What is the relationship between meaning, resiliency, and psychological flexibility?
- Hypothesis: These should be highly correlated.

## Materials

- Resiliency Scale 14 Items (Wagnild, 2009)
- Meaning in Life Scale (Steger et al., 2006)
- Multidimensional Psychological Flexibility Inventory (Rolffs et al., 2018)

## Correlation stuff 




## Check type

## How to Implement

## How to Score

## What Happened? 
